Measurement and Probability in Fuzzy Quantum Theories

### 2017-06-29 prop_iop.tex
prop_iop.tex \subsubsection{Sates Consistent with a QIVPM Induced by the Born Rule} Updating...

\begin{definition}\cite{544199} Given a operator or matrix\nb$\rho$,
the norm of $\rho$ is defined by 
\begin{equation}
\left\Vert \rho\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho}{\psi}\right|\,.
\end{equation}
\footnote{Notice that it doesn't have square root, and this definition only
appears in \cite{544199}... Need to this definition in other sources.}\end{definition}

>>>>

\begin{definition}\cite{544199} Given a operator or matrix\nb$A$,
the norm of $A$ is defined by 
\begin{equation}
\left\Vert A\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{A}{\psi}\right|\,.
\end{equation}
\end{definition}

The previously defined matrix norm is not one of the common matrix
norms as in the following example.

\begin{example}Consider $A=\left(\begin{array}{cc}
1 & 0\\
1 & 1
\end{array}\right)$. Then, 
\begin{equation}
\left\Vert A\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{A}{\psi}\right|=\frac{3}{2}\,.
\end{equation}
\end{example}
